---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![DOI](http://joss.theoj.org/papers/10.21105/joss.01041/status.svg)](https://doi.org/10.21105/joss.01041) [![Build Status](https://travis-ci.org/daijiang/hillR.svg?branch=master)](https://travis-ci.org/daijiang/hillR) [![Coverage status](https://codecov.io/gh/daijiang/hillR/branch/master/graph/badge.svg)](https://codecov.io/github/daijiang/hillR?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/hillR)](https://cran.r-project.org/package=hillR)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/hillR)](http://www.r-pkg.org/pkg/hillR)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/grand-total/hillR?color=green)](http://www.r-pkg.org/pkg/hillR)

# hillR

This package contains R functions to calculate taxonomic, functional, and phylogenetic diversity and site similarity through Hill Numbers. The underlying methods are based on Chao, Chiu and Jost 2014 and Chiu & Chao 2014.

# Installation

To install this package, run the following code:

```{r, eval=FALSE}
install.packages("hillR")
# or install from Github
devtools::install_github("daijiang/hillR")
```

# Examples

```{r data}
dummy = FD::dummy
comm = dummy$abun
traits = dummy$trait
tree = ape::rtree(n = ncol(comm), tip.label = paste0("sp", 1:ncol(comm)))
library(hillR)
```

## Calculate taxonomic, functional, and phylogenetic diversity of each site

```{r}
hill_taxa(comm, q = 0) # taxonomic alpha diversity

hill_func(comm, traits, q = 0) # functional alpha diversity

hill_phylo(comm, tree, q = 0) # phylogenetic alpha diversity
```

## Calculate taxonomic, functional, and phylogenetic diversity across multiple sites

```{r}
hill_taxa_parti(comm, q = 0) # taxonomic diversity across all sites

hill_func_parti(comm, traits, q = 0) # functional diversity across all sites

hill_phylo_parti(comm, tree, q = 0) # phylogenetic diversity across all sites
```

## Calculate pairwise taxonomic, functional, and phylogenetic diversity

```{r}
hill_taxa_parti_pairwise(comm, q = 0, show.warning = F) # pairwise taxonomic diversity

hill_func_parti_pairwise(comm, traits, q = 0, show.warning = F) # pairwise functional diversity

hill_phylo_parti_pairwise(comm, tree, q = 0, show.warning = F) # pairwise phylogenetic diversity
```
    
# Licenses

Licensed under the [MIT license](LICENSE). ([More information here](http://en.wikipedia.org/wiki/MIT_License).)

# Citation

Please cite this package if you use it. The citation information can be obtained by running `citation('hillR')` in R.

> Li, (2018). hillR: taxonomic, functional, and phylogenetic diversity and similarity through Hill Numbers. Journal of Open Source Software, 3(31), 1041. https://doi.org/10.21105/joss.01041

```bibtex
@Article{,
    title = {hillR: taxonomic, functional, and phylogenetic diversity and similarity through Hill Numbers},
    author = {Daijiang Li},
    journal = {Journal of Open Source Software},
    year = {2018},
    volume = {3},
    number = {31},
    pages = {1041},
    url = {https://doi.org/10.21105/joss.01041},
 }
```


# Reference

- [Chao, Anne, Chun-Huo Chiu, and Lou Jost. “Unifying Species Diversity, Phylogenetic Diversity, Functional Diversity, and Related Similarity and Differentiation Measures Through Hill Numbers.” Annual Review of Ecology, Evolution, and Systematics 45, no. 1 (2014): 297–324. doi:10.1146/annurev-ecolsys-120213-091540.](https://doi.org/10.1146/annurev-ecolsys-120213-091540)
- [Chiu, Chun-Huo, and Anne Chao. “Distance-Based Functional Diversity Measures and Their Decomposition: A Framework Based on Hill Numbers.” PLoS ONE 9, no. 7 (July 7, 2014): e100014. doi:10.1371/journal.pone.0100014.](https://doi.org/10.1371/journal.pone.0100014)

# Contributing

Contributions are welcome. You can provide comments and feedback or ask questions by filing an issue on Github [here](https://github.com/daijiang/hillR/issues) or making pull requests. 
